\section{Problem 4 (2 points)}

\begin{align*}
    y[n]&=x[n]+2 x[n-1]+x[n-2] \\y[n]&=-0.9 y[n-1]+x[n] .
\end{align*}

\subsection*{(a)Find the unit pulse responses $h_1[n]$ and $h_2[n]$ of the systems.}

The unit pulse response $h[n]$ of a system is the output whenever ethe input is a unit pulse $\delta[n]$, which is 1 at n=0 and 0 everywhere else.

\begin{equation*}
    \delta[n] = 
    \begin{cases} 
        1, & \text{if } n = 0 \\
        0, & \text{otherwise}
    \end{cases}
\end{equation*}

by substituting $x[n]$ with $\delta[n]$ we get:

\begin{align*}
    h_1[n]&=\delta[n]+2 \delta[n-1]+\delta[n-2] \\h_2[n]&=-0.9 h_2[n-1]+\delta[n] .
\end{align*}

\subsection*{(b) State whether each system is FIR or IIR. Justify your answer.}

The first system unit pulse response will eventually become zero as the impulse response only depends on the current and past inputs, therefore it is a FIR system. The second system on the other hand will have a unit pulse system that continues indefinitly as the you have to consider the previous outputs $y_2[n-1]$ to find the impulse response $h_2[n]$. This means that this system is IIR.

\subsection*{(c) Determine whether each system is stable.}

A system is bounded-input bounded-output stable (BIBO) if

\begin{equation*}
    |x[n]| \leq M_{x}<\infty \Rightarrow|y[n]| \leq M_{y}<\infty \Rightarrow, \forall n
\end{equation*}

The first system is an FIR system and has finite coefficients, therefore the system wil produce a bounded output for any bounded input.

The second system is a IIr system